### 2012-06-05 docs/makefiles/makefiles.tex
new build system

  This variable points to the path (relative to {\tt fParallel/}) of
  the equation of state used for the build.  Choices that work
  with \maestro\ are:
  \begin{itemize}
  \item {\tt extern/EOS/helmeos}
  \item {\tt extern/EOS/gamma\_law\_general}
  \end{itemize}

@@

  This variable points to the conductivity routine used for the build
  (relative to {\tt fParallel/}).  Choices that work with \maestro\
  are:
  \begin{itemize}
  \item {\tt extern/conductivity/constant}
  \item {\tt extern/conductivity/timmes\_stellar}
  \end{itemize}
  If diffusion is not being used for the problem, this should be set
  to {\tt extern/conductivity/constant}.

@@

  This variable points to the reaction network used for the build
  (relative to {\tt fParallel/}).  A lot of options are present in
  {\tt extern/networks/}.  A network is required even if you are not
  doing reactions, since the network defines the species that are
  advected and interpreted by the equation of state.

@@

>>>>

  This variable points to the directory (by default, relative to {\tt Microphysics/EOS/}) of
  the equation of state used for the build.  Choices that work
  with \maestro\ are:
  \begin{itemize}
  \item {\tt extern/EOS/helmeos}
  \item {\tt extern/EOS/gamma\_law\_general}
  \end{itemize}
  To use an EOS contained in a different location, set the variable {\tt EOS\_TOP\_DIR}
  to point to the directory above the alternate EOS directory.

@@

  This variable points to the conductivity routine used for the build
  (by default, relative to {\tt Microphysics/conductivity/}).  Choices
  that work with \maestro\ are: 
  %
  \begin{itemize} 
  \item {\tt extern/conductivity/constant} 
  \item {\tt extern/conductivity/timmes\_stellar} 
  \end{itemize} 
  % 
  If diffusion is not being used for the problem, this should be set
  to {\tt extern/conductivity/constant}.  To use an alternate conductivity
  routine, set the variable {\tt CONDUCTIVITY\_TOP\_DIR} to point
  to the directory above the alternate conductivity directory.

@@

  This variable points to the reaction network used for the build (by
  default, relative to {\tt Microphysics/networks/}).  Several options
  are present in {\tt extern/networks/}.  A network is required even
  if you are not doing reactions, since the network defines the
  species that are advected and interpreted by the equation of state.

@@

  To use an alternate reaction network, set the variable {\tt
  NETWORK\_TOP\_DIR} to point to the directory above the alternate
  network.
